Robust Estimation, Prediction and Control with \\ Linear Dynamics and Arbitrary Costs

### 2020-01-16 main.tex
Updates from Overleaf

\begin{definition}[Robust sequence upper bounds] We define an upper-bound for the value of sequences of actions:
\begin{equation}
\label{eq:robust_sequence_ucb}
b_i^r(n)  \eqdef
\begin{cases}
\min_{m\in[1, M]} \sum_{t=0}^{d-1} \gamma^t r_t^m  + \frac{\gamma^d}{1-\gamma} &\text{if } i \in \mathcal{L}_n \text{ ;}\\
\max_{a\in\mathcal{A}} b_{ia}^r(n) & \text{if } i \in \mathcal{T}_n \setminus \mathcal{L}_n 
\end{cases}
\end{equation}
where $r_t^m$ is the reward obtained at step $t$ by following $i$ with dynamics $f^m$.
\end{definition}
An illustration of the computation of the robust b-values is presented in Figure \ref{fig:drop}.

\begin{figure}
\centering
\includegraphics[width=0.4\linewidth]{img/robust-control-tree}
\caption{The computation of robust b-values in Algorithm \ref{algo:drop}. The simulation of trajectories for every dynamics model $f^m$ is represented as stacked versions of the expanded tree $\mathcal{T}_n$.}
\label{fig:drop}
\end{figure}

@@

We introduce a measure of the problem difficulty: TODO: Definition of $\kappa\in [1, K]$
A node $i\in\mathcal{T}$ is said to be $\epsilon$-optimal, in a robust sense, if and only if $V_i^r \geq V^r - \epsilon$ for some $\epsilon > 0$. The proportion of $\epsilon$-optimal nodes at depth $d$ is then defined as $p_d(\epsilon) = |i \in \mathcal{A}^d$ s.t $i$ is $\epsilon$-optimal$|/K^d$. Further we will assume that for the graph $\mathcal{T}$ the following hypothesis is satisfied:

>>>>

\begin{definition}[Robust sequence upper bounds] We define an upper-bound for the value of sequences of actions:
\begin{equation}
\label{eq:robust_sequence_ucb}
b_i^r(n)  \eqdef
\begin{cases}
\min_{m\in[1, M]} \sum_{t=0}^{d-1} \gamma^t R_t^m  + \frac{\gamma^d}{1-\gamma} &\text{if } i \in \mathcal{L}_n \text{ ;}\\
\max_{a\in\mathcal{A}} B_{ia}^r(n) & \text{if } i \in \mathcal{T}_n \setminus \mathcal{L}_n 
\end{cases}
\end{equation}
where $R_t^m$ is the reward obtained at step $t$ by following $i$ with dynamics $f^m$.
\end{definition}
An illustration of the computation of the robust b-values is presented in Figure \ref{fig:drop}.

\begin{figure}
\centering
\includegraphics[width=0.4\linewidth]{img/robust-control-tree}
\caption{The computation of robust B-values in Algorithm \ref{algo:drop}. The simulation of trajectories for every dynamics model $f^m$ is represented as stacked versions of the expanded tree $\mathcal{T}_n$.}
\label{fig:drop}
\end{figure}

@@

We express the performance of the planning problem in terms of a measure of the proportion of near-optimal paths:
\[
\kappa = \limsup_{h\rightarrow\infty} \left|\left\{a\in A^h: V(a)\geq V - \frac{\gamma^{h+1}}{1-\gamma}\right\}\right|^{1/h}.
\]
